Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-01-26 string_physics_educator_revision2.tex
fixes #27

\noindent Solutions to equation~\ref{rdashdash} correspond to a taut
string confined to Flamm's paraboloid~\cite{flamm1916}; see
Figure~\ref{flamm}.  It is interesting to compare
equation~\ref{rdashdash} with the corresponding equation for null
geodesics, which is usually given~\cite{wald} in terms of $u=2M/r$ as
$u''=3u^2/2-u$, but is equivalent
to~$r''\left(\phi\right)=r-3M+2\left(r'\right)^2/r$.  This shows that
light, being sensitive to the time component of the metric, behaves
differently from string, which is not (at this point it might be worth
``reminding'' students that a straight line in flat space,
$r=r_0\sec\left(\phi-\phi_0\right)$, obeys
$r''=r+2\left(r'\right)^2/r$).

>>>>

\noindent Solutions to equation~\ref{rdashdash} correspond to a taut
string confined to Flamm's paraboloid~\cite{flamm1916}; see
Figure~\ref{flamm}.  It is interesting to compare
equation~\ref{rdashdash} with the corresponding equation for
equatorial null geodesics, which is usually given~\cite{wald} in terms
of $u=2M/r$ as $u''=3u^2/2-u$, but is equivalent
to~$r''\left(\phi\right)=r-3M+2\left(r'\right)^2/r$.  This shows that
light, being sensitive to the time component of the metric, behaves
differently from string, which is not (at this point it might be worth
``reminding'' students that a straight line in flat space,
$r=r_0\sec\left(\phi-\phi_0\right)$, obeys
$r''=r+2\left(r'\right)^2/r$).
